Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-07-01 article.rnw
Fix an error in the subcaptiosn of the best alpha matrix figure.
I had the captions of the row and column coclassification matrices interchanged.
Standardise the subcaptions of coclassification matrix figures.
In one figure it was rows/columns; in the other it was effects/responses.
Now both are effects/responses, with rows/columns in brackets where necessary.
Move the heavy analysis currently in the rnw file into a separate R script which saves an rda.
This speeds up compilation, by not requiring all the analysis to be rerun
every time the wording of the article changes.
It also allows the sa

<<include=FALSE>>=
	source("r/parameters.R")
	source("r/input-data.R")
	source("r/post-process.R")
	source("r/brute-post-process.R")
	source("r/mantel-test.R")
	source("r/dist-matrix.R")
	source("r/coclassification-table.R")
	source("r/grouped-matrix.R")

	species_dat <- read.csv("data/species.csv")
	species_output_order <- c(4,3,1,2,6,5)

	input_data <- InputData$new("output/focal-vector.data", "output/response-vector.data", "output/design-matrix.data", is_per_capita=TRUE)

	num_species <- input_data$num_species
	num_obs <- input_data$num_obs

	ic <- "aicc" #The information criterion to use, e.g. "aic" or "aicc"
	ic_weight <- sprintf("%s_weight", ic)
	ic_name <- list(aic="AIC", aicc="AICc")[[ic]]

	brute_data <- BruteData$new("output/brute.data", species_dat$name, ic_weight)

	#Precalculate the coclassification matrices, as these are active bindings and the slowest part of compilation.
	weighted_col_coclassification_matrix <- brute_data$weighted_col_coclassification_matrix
	weighted_row_coclassification_matrix <- brute_data$weighted_row_coclassification_matrix

	#Precalculate distances matrices as well.
	col_distance_matrix <- 1 - weighted_col_coclassification_matrix
	row_distance_matrix <- 1 - weighted_row_coclassification_matrix
	body_weight_distance_matrix <- build_dist_matrix(species_dat$name, species_dat$body_weight, function(w1,w2){abs(w1-w2)})
@

@@

	\begin{subfigure}{0.49\textwidth}
		\centering
		<<>>=
			minimal_coclassification_kable(
				best_col_coclassification,
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Coclassification matrix of rows}
		\label{fig:best-coclassification-cols}
	\end{subfigure}
	%
	\begin{subfigure}{0.49\textwidth}
		\centering
		<<>>=
			minimal_coclassification_kable(
				best_row_coclassification,
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Coclassification matrix of columns}
		\label{fig:best-coclassification-rows}
	\end{subfigure}

@@

% DBS: Adding a new note here. Shouldn't we pick one version that gets used in Fig 2 and in Fig 3 to refer to the two coclassification matrices?

>>>>

<<include=FALSE>>=
	library(magrittr)
	load("output/article-data.rda")
@

@@

	\begin{subfigure}{0.49\textwidth}
		\centering
		<<>>=
			minimal_coclassification_kable(
				best_col_coclassification,
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Coclassification of competitive effects\\(columns)}
		\label{fig:best-coclassification-cols}
	\end{subfigure}
	%
	\begin{subfigure}{0.49\textwidth}
		\centering
		<<>>=
			minimal_coclassification_kable(
				best_row_coclassification,
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Coclassification of competitive responses\\(rows)}
		\label{fig:best-coclassification-rows}
	\end{subfigure}

@@
